---
title: "Survey Results"
output: 
  html_document:
    toc: yes
    toc_float:
      collapsed: true
---

```{r, include=F, warning=F}
#rmarkdown::render("L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/B Analysis/R/1. R Scripts/src/summary_by_country.Rmd", clean=TRUE,output_format='html_document',output_file='L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/B Analysis/R/4. Results/summary_by_country.html')
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(stringr)  # For wrapping long titles

# Load the combined dataset and question text
df <- readRDS("L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/B Analysis/R/2. Datasets/combined.RDS")
question_text <- read.csv("L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/A Source documents/iDPS - Variable list/questions.csv")

# Remove ".FI" from question names in both df and question_text
df$Question <- gsub("\\.FI$", "", df$Question)
question_text$Variable <- gsub("\\.FI$", "", question_text$Variable)

# Clean up and prepare the question_text dataset
question_text <- question_text %>%
  distinct(Variable, .keep_all = TRUE) %>%
  filter(Variable %in% df$Question)

# Merge df and question_text based on df$Question and question_text$Variable
df <- merge(df, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE)

# Filter rows where all countries have TRUE in the presence columns
presence_columns <- c("NL", "FR", "SWE", "FIN", "JPN")
df <- df %>% filter(across(all_of(presence_columns), ~ . == TRUE))

# Replace country codes with actual country names
country_mapping <- c("NL" = "Netherlands", "FR" = "France", "SWE" = "Sweden", 
                     "FIN2" = "Finland", "JPN" = "Japan")
df$Country <- country_mapping[df$country]

# Set up a new color palette for countries
country_colors <- c(
  "Netherlands" = "#FF6600", # Orange for NL
  "France" = "#1E90FF",      # Blue for France
  "Sweden" = "#FFD700",      # Yellow for Sweden
  "Finland" = "#0000FF",     # Blue for Finland
  "Japan" = "#FF0000"        # Red for Japan
)

# Ensure the Country and Response columns are treated as factors
df$Country <- as.factor(df$Country)
df$Response <- as.factor(df$Response)

# Extract unique questions
questions <- sort(unique(df$Question))
```

```{r plots, warning = F, results="asis", echo=FALSE, include= T, results="asis"}
# Initialize a vector to keep track of processed main questions
processed_questions <- c()

# Loop over each question
for (question in questions) {
  
  # Retrieve the corresponding Question_Text for the current question
  question_text_value <- question_text %>%
    filter(Variable == question) %>%
    pull(Question_Text)

  # Handle cases where Question_Text is missing
  if (length(question_text_value) == 0 || is.na(question_text_value)) {
    question_text_value <- "Unknown Question"
  }

  # Split the question text by either ':' or '?'
  split_question <- unlist(strsplit(question_text_value, "[:?]"))
  main_question <- trimws(split_question[1])  # First part
  sub_question <- trimws(split_question[2])    # Second part (if it exists)

  # Check if the main question has already been processed
  if (!main_question %in% processed_questions) {
    # Print the main question as a first-level header (for TOC)
    cat(paste0("# ", main_question, "\n\n"))
    # Mark this question as processed
    processed_questions <- c(processed_questions, main_question)
  }

  # Print the sub-question as a second-level header (for TOC), if it exists
  if (!is.na(sub_question) && nchar(sub_question) > 0) {
    cat(paste0("## ", sub_question, "\n\n"))
  }

  # Filter the data for the current question
  data_filtered <- df %>%
    filter(Question == question) %>%
    group_by(Country, Response) %>%
    summarise(Count = sum(Count), .groups = 'drop') %>%
    group_by(Country) %>%
    mutate(Percentage = 100 * Count / sum(Count))
  
  # Wrap long response labels
  data_filtered$Response <- str_wrap(as.character(data_filtered$Response), width = 30)

  # Create the plot
  p <- ggplot(data_filtered, aes(x = Response, y = Percentage, fill = Country)) +
    geom_bar(stat = "identity", position = "dodge") +
    facet_wrap(~ Country, scales = "free_y") +
    scale_fill_manual(values = country_colors) +
    labs(title = main_question, x = "Response", y = "Percentage") +
    coord_flip() +
    theme_light() +
    theme(legend.position = "none",
          axis.text.y = element_text(angle = 0, hjust = 1),
          plot.title = element_text(size = 14)) +
    scale_y_continuous(labels = scales::percent_format(scale = 1))

  # Print the plot
  print(p)
  
    # Ensure proper spacing after each plot
  cat("\n\n")  # Add additional line breaks after each plot for spacing
}