---
title: "Donor iron supplement perception: classify donors FI"
author: "Mikko Arvas"
date: "`r Sys.time()`"
output:
  html_document:
    toc: true
    theme: united
---





```{r setup, include=FALSE}
#echo "rmarkdown::render('summarise_data.Rmd', clean=TRUE,output_format='html_document',output_file='../results/summarise_data.html')" | R --slave
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(gtsummary)
library(likert)
#library(poLCA)
library(tidySEM)
```



```{r}
load("../data/donorironpercep.rdata")

#We only want to look at blood donors
data <- data %>% 
  filter(!`8: How many times have you donated whole blood in your lifetime?` == "None")

```


# Donation symptoms

## Occurence

```{r , warning=FALSE}
items = data %>% 
    dplyr::select(which(str_detect(colnames(data) ,"^11\\.\\d"))) 

colnames(items) <- str_remove(string = colnames(items),pattern = ".*\\?") %>% 
  str_remove(".*:") %>% 
  str_remove("^ ") %>% 
  str_replace_all(" ","_")

nlevels = 4

levels(data$`11.1: Bruises at the location where the needle was inserted`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```





```{r}
x <- mxFactor(items,levels=c("Never", "Sometimes", "Often", "Always"),labels=c(1,2,3,4))
```


```{r}
df_plot <- x
#names(df_plot) <- paste0("Value.", names(df_plot))
df_plot <- pivot_longer(x,cols = all(x))
ggplot(df_plot, aes(x = Value)) + geom_bar() + facet_wrap(~time,
    scales = "free") + theme_bw()
```


```{r}
desc <- tidySEM::descriptives(na.omit(x))
desc <- desc[, c("name", "type", "n", "missing", "unique", "mode",
    "mode_value", "v")]
desc
```


```{r}
set.seed(123)
res <- mx_lca(data = na.omit(x), classes = 4)

```


```{r}
items = data %>% 
    dplyr::select(which(str_detect(colnames(data) ,"^11\\.\\d"))) 

colnames(items) <- str_remove(string = colnames(items),pattern = ".*\\?") %>% 
  str_remove(".*:") %>% 
  str_remove("^ ") %>% 
  str_replace_all(" ","_") %>%
  str_replace_all("_.*","") %>%
  na.omit()

f <- paste(paste(colnames(items),collapse = " + ")," ~ 1")

lc2 <- poLCA(f,items,nclass=2)
```


```{r}
data("carcinoma")
class(carcinoma)
```

```{r}
summary(carcinoma)
```



```{r}
f <- cbind(A,B,C,D,E,F,G)~1
lc2 <- poLCA(f,carcinoma,nclass=2)
```



## Severity


```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^12\\.\\d"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 6

levels(data$`12.10: Please indicate the severity of the symptoms? Thirst`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

# Donation knowledge

## General



```{r , warning=FALSE}
items = data %>% 
    select(which(str_detect(colnames(data) ,"^13\\.\\d"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`13.1: During each donation, a donor gives approximately 500ml (16 oz.) of blood`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```




```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^14\\.\\d"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`14.1: During each donation, a donor gives approximately 500ml (16 oz.) of blood`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```



## Hemoglobin



```{r , warning=FALSE}
items = data %>% 
    select(which(str_detect(colnames(data) ,"^15\\.\\d"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`15.2: Hemoglobin transports oxygen through the body`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```




```{r , warning=FALSE}
items = data %>% 
    select(which(str_detect(colnames(data) ,"^16\\.\\d"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`16.2: Hemoglobin transports oxygen through the body`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```





## Ferritin



```{r , warning=FALSE}
items = data %>% 
    select(which(str_detect(colnames(data) ,"^17\\.\\d"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`17.1: Iron is needed for the production of hemoglobin in the body`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```




```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^18\\.\\d"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`18.1: Iron is needed for the production of hemoglobin in the body`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


## Measurements

```{r , warning=FALSE}
items = data %>% 
    select(which(str_detect(colnames(data) ,"^19\\.\\d"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`19.1: Are any of the following blood values measured by FRCBS before, during or after donation? Hemoglobin (Hb)`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```



## Process


```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^20"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`20: What happens if a donor has a low hemoglobin value prior to donating? Hemoglobin is not measured`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

# Hb-deferral

## Occurence

```{r}

data %>% count(`21: Have you ever been deferred or ineligible to donate due to low hemoglobin?`)

```

## Last time

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^22"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`22: When was your last deferral? 1-2 years ago`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


## Was the information about deferral ...

```{r , warning=FALSE}
items = data %>% 
    select(which(str_detect(colnames(data) ,"^23"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 5

levels(data$`23.1: Was the information you received about your deferral from the blood service: Understandable`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

```{r}
library(tidySEM)
#This works
items = data %>% 
    dplyr::select(which(str_detect(colnames(data) ,"^23"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

colnames(items)  <- str_remove(colnames(items),pattern = "^.*: ")

df <- items
colnames(df) <- c("A","B","C","D","E")

df <- mxFactor(na.omit(df),levels=c(1,2,3,4,5))
descriptives(df)
```

```{r}
table(df$A)
```


```{r}
table(df$B)

```

```{r}
dim(df)
```



```{r}

#set.seed(42)
res <- mx_lca(data = df, classes = 1:3)

```

```{r}

#x <- sample( LETTERS[1:4], 10000, replace=TRUE, prob=c(0.1, 0.2, 0.65, 0.05) )

```

## Missing information

```{r}

table2 <-
  tbl_summary(
    data2,
    include = c(
      Which_information_was_missing_from_the_information_you_received_about_your_deferral_from_the_blood_service
            ),
    #by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2


```


## Effect to motivation

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^25|^26"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 5

levels(data$`26: If you would be deferred due to low hemoglobin, what effect would this have on your motivation to continue to donate?`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

# Iron deficiency 

## Symptoms

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^27"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`27: Do you know what possible symptoms of iron deficiency (a lack of iron in the body) are? Dark stool`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```




```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^27"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`27: Do you know what possible symptoms of iron deficiency (a lack of iron in the body) are? Dark stool`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

## Replacement



```{r}

table2 <-
  tbl_summary(
    data2,
    include = c(
      When_you_donate_blood_you_lose_some_iron_as_well_do_you_do_anything_before_you_donate_to_help_to_manage_any_iron_lose,
      How_do_you_take_the_amount_of_iron_you_lose_during_a_donation_into_account
            ),
    #by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2


```

## Information

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^30"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`27: Do you know what possible symptoms of iron deficiency (a lack of iron in the body) are? Dark stool`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


# Opinion on supplements

## Iron

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^32"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 5

levels(data$`32.1: What is your opinion on the use of iron supplements? Bad (1) -  Good (5)`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

## Dietary


```{r}
table2 <-
  tbl_summary(
    data2,
    include = c(
      Do_you_take_dietary_supplements_containing_vitamin_D,
      Do_you_take_other_dietary_supplements
            ),
    #by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2

```




```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^35"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`35.1: Why did/do you take dietary supplements? It was advised by a professional`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


```{r}
data %>% count(`36: Is there a different reason why you use(d) dietary supplements?`)
```

## Iron statements

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^38"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`38.1: Are the following statements about iron supplements true or false? Iron supplements are provided by the blood service to donors with reduced iron levels`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^39"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`39.1: Are the following statements about iron supplements true or false? confidence Iron supplements are provided by the blood service to donors with reduced iron levels`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


## Iron side effects


```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^40"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`39.1: Are the following statements about iron supplements true or false? confidence Iron supplements are provided by the blood service to donors with reduced iron levels`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

## Iron use

```{r}

table2 <-
  tbl_summary(
    data2,
    include = c(
      Have_you_ever_taken_or_are_you_currently_taking_iron_supplements
            ),
  #  by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2


```



```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^42"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 3

levels(data$`42.1: What experiences do you have with iron supplements? Physical fitness`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


## Iron concerns

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^43"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`43.1: Do you have any concerns about iron supplements? I don’t know whether iron supplements can be harmful to my health`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

## Reaction to offering iron

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^45"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 5

levels(data$`45.1: If the blood service would offer iron supplements to me, then I would gladly make use of this`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```



```{r}


data %>% count(`46: What would be your most important reason to take iron supplements if they would be / when they have been provided to me by your blood service?`)

```

## Reason to use iron



```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^47"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 5

levels(data$`47.1: Suppose it turns out that your iron level is too low, which of the following options would you prefer? A longer interval between donations to replenish my iron stores`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

"Please drag the options in the right order, with 1 being most preferred and 5 least preferred option"



## Willingness to use iron

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^48"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`48.1: If the blood service would provide / has provided iron supplements to you, in what situation are you most willing to use them? If I would have health complaints which could be resolved by this`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

## Bases for policy


```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^49"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 6

levels(data$`49.1: What do you think is most important when considering iron supplementation as a blood service policy for donors with low iron levels? That donors can continue to donate without larger donation intervals`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

"Please drag the options in the right order, with 1 being most preferred and 5 least preferred option"


