---
title: "Donor iron supplement perception data summary across countries"
author: "Amber Meulenbeld"
date: "`r Sys.time()`"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
#rmarkdown::render("L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/B Analysis/R/1. R Scripts/src/summarise_data_across_countries.Rmd", clean=TRUE,output_format='html_document',output_file='L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/B Analysis/R/4. Results/summarise_data_across_countries.html')
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(readxl)
library(dplyr)

```



```{r, echo=F}
currentDate <- format(Sys.time(), "%Y-%m-%d")
FolderName <- paste("L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/B Analysis/R/3. Plots/", currentDate,sep="")
dir.create(FolderName)

# Read in combined country data 
data <- readRDS("L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/B Analysis/R/2. Datasets/combined.RDS") %>% mutate(country = ifelse(country == "FIN2", "FIN", country)) %>% group_by(Question, country, Response) %>%
    summarise(Count = sum(Count), .groups = 'drop') %>%
    group_by(Question, country) %>%
    mutate(Percentage = 100 * Count / sum(Count)) %>%
    ungroup()

#Change country codes to full names
country_mapping <- c("NL" = "Netherlands", "FR" = "France", "SWE" = "Sweden", 
                     "FIN" = "Finland", "JPN" = "Japan")
data$Country <- country_mapping[data$country]
country_colors <- c(
  "Netherlands" = "#E69F00", # Orange (Colorblind-friendly orange)
  "France"      = "#0072B2", # Blue (Colorblind-friendly blue)
  "Sweden"      = "#F0E442", # Yellow (Colorblind-friendly yellow)
  "Finland"     = "#56B4E9", # Sky blue (Colorblind-friendly cyan)
  "Japan"       = "#D55E00"  # Red (Colorblind-friendly reddish-brown)
)


#read in questions
question_text <- read.csv("L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/A Source documents/iDPS - Variable list/questions.csv")


```

# Characteristics

## Age

```{r, echo=F}
q <- data %>% filter(grepl("^Age$", Question))

#manually add row for NL for aesthetic reasons
new_row <- data.frame(Question = "Age", country = "NL", Response = "18-20", 
                      Count = 0, Percentage = 0, Country = "Netherlands", stringsAsFactors = FALSE)

q <- rbind(q, new_row)

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    #Statement = sub(".*?, then (.*)", "\\1", Question_Text),
    #Q = "Are the following statements True or False?", #sub("(.*), then.*", "\\1", Question_Text),
    answer = factor(Response, levels = c("18-20", "17-20", "[18,25]", "21-30", "(25,35]", 
                                          "31-40", "(35,45]", "41-50", "(45,55]", 
                                          "51-60", "(55,65]", "61-70", "(65,68]", "71-80"))
  )

#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = Percentage, y = answer, fill = Country)) +  # Swapped x and y
  facet_wrap(~ Country, scales = "free_y", strip.position = "top", nrow=1) +  # Use facet_wrap and free_y
  xlab("Percentage") +  # Label for x-axis (Percentage)
  ylab(" ") +           # Empty y label
  ggtitle(unique(qdata$Question_Text)[1]) +
  scale_x_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120)) +  # Set x scale for Percentage
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0),  # Keeps facet text horizontal
    strip.placement = "outside",                  # Places facet labels outside
    strip.text = element_text(size = 12)          # Adjust facet label size for clarity
  ) +
  geom_text(aes(x = Percentage, y = answer, label = round(Percentage, 1)), 
            hjust = -0.5, size = 3) +  # Adjust for horizontal text justification
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))  # Set y scale with wrapped text

p

FileName <- paste(FolderName, "/Age - by country.png",sep="")
ggsave(FileName, width = 10, height = 3)
```

## Sex

```{r, echo=F}
q <- data %>% filter(grepl("^Sex$", Question))



qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    #Statement = sub(".*?, then (.*)", "\\1", Question_Text),
    #Q = "Are the following statements True or False?", #sub("(.*), then.*", "\\1", Question_Text),
    answer = factor(Response, levels = c("Prefer not to say", "Other", "Non-binary", "Male", "Female" ))
  )

#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = Percentage, y = answer, fill = Country)) +  # Swapped x and y
  facet_wrap(~ Country, strip.position = "top", nrow=1) +  # Use facet_wrap and free_y
  xlab("Percentage") +  # Label for x-axis (Percentage)
  ylab(" ") +           # Empty y label
  ggtitle(unique(qdata$Question_Text)[1]) +
  scale_x_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120)) +  # Set x scale for Percentage
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0),  # Keeps facet text horizontal
    strip.placement = "outside",                  # Places facet labels outside
    strip.text = element_text(size = 12)          # Adjust facet label size for clarity
  ) +
  geom_text(aes(x = Percentage, y = answer, label = round(Percentage, 1)), 
            hjust = -0.5, size = 3) +  # Adjust for horizontal text justification
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))  # Set y scale with wrapped text

p

FileName <- paste(FolderName, "/Sex - by country.png",sep="")
ggsave(FileName, width = 10, height = 3)
```

# Deferral

## Been deferred?

```{r, echo=F}
q <- data %>% filter(grepl("^Deferral$", Question))



qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    #Statement = sub(".*?, then (.*)", "\\1", Question_Text),
    #Q = "Are the following statements True or False?", #sub("(.*), then.*", "\\1", Question_Text),
    answer = factor(trimws(Response), levels = c("I don’t know", "No", "Yes, multiple times", "Yes, once"))
  )

#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = Percentage, y = answer, fill = Country)) +  # Swapped x and y
  facet_wrap(~ Country, strip.position = "top", nrow=1) +  # Use facet_wrap and free_y
  xlab("Percentage") +  # Label for x-axis (Percentage)
  ylab(" ") +           # Empty y label
  ggtitle(str_wrap(unique(qdata$Question_Text)[1], width = 75)) +
  scale_x_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120)) +  # Set x scale for Percentage
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0),  # Keeps facet text horizontal
    strip.placement = "outside",                  # Places facet labels outside
    strip.text = element_text(size = 12)          # Adjust facet label size for clarity
  ) +
  geom_text(aes(x = Percentage, y = answer, label = round(Percentage, 1)), 
            hjust = -0.5, size = 3) +  # Adjust for horizontal text justification
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))  # Set y scale with wrapped text

p

FileName <- paste(FolderName, "/Deferral - by country.png",sep="")
ggsave(FileName, width = 10, height = 3)
```

## Deferral source

```{r, echo=F}
q <- data %>% filter(grepl("DeferralSource([1-7]|6A|2.NL)$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("TRUE", "FALSE", "Yes", "No"))
  ) %>% filter(Response == "Yes" | Response == "TRUE") %>% mutate(Statement = ordered(Statement, levels = c(" Blood service staff", " Blood service website and/or brochure", " Donor physician"," Health care practitioner", " Search information on the internet", " Other, namely", " None")))

#Faceted by country
p <- ggplot(qdata) + 
  geom_bar(aes(x = Statement, y = Percentage, fill = Country), 
           position = 'dodge', stat = "identity") + 
  # facet_grid(Statement ~ ., 
  #            labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
  #            switch = "y",
  #            scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1],"?"), width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "left") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  #guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = Statement, y = Percentage, label = round(Percentage, 1), group = Country), 
            vjust = -0.5, size = 3, 
            position = position_dodge(width = 0.9)) + # Use dodge to align text with bars
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))


p

FileName <- paste(FolderName, "/DeferralSource - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```


## Deferral Info

```{r, echo=F}
q <- data %>% filter(grepl("^DeferralInfo[1-9]$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c(1,2,3,4,5))
  )


#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(unique(qdata$Q)[1])+
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/DeferralInfo - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)

```

## Deferral source

```{r, echo=F}
q <- data %>% filter(grepl("^LackDeferralInfo([1-5])$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("TRUE", "FALSE", "Yes", "No"))
  ) %>% filter(Response == "Yes" | Response == "TRUE") 


#Faceted by country
p <- ggplot(qdata) + 
  geom_bar(aes(x = Statement, y = Percentage, fill = Country), 
           position = 'dodge', stat = "identity") + 
  # facet_grid(Statement ~ ., 
  #            labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
  #            switch = "y",
  #            scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1],"?"), width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "left") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  #guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = Statement, y = Percentage, label = round(Percentage, 1), group = Country), 
            vjust = -0.5, size = 3, 
            position = position_dodge(width = 0.9)) + # Use dodge to align text with bars
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))


p

FileName <- paste(FolderName, "/LackDeferralInfo - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```
# Iron Loss

## Account for Iron Loss

```{r, echo=F}
q <- data %>% filter(grepl("^AccForIronLoss$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("TRUE", "FALSE", "Yes", "No"))
  ) 


#Faceted by country
p <- ggplot(qdata) + 
  geom_bar(aes(x = answer, y = Percentage, fill = Country), 
           position = 'dodge', stat = "identity") + 
  # facet_grid(Statement ~ ., 
  #            labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
  #            switch = "y",
  #            scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1],"?"), width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "left") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  #guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1), group = Country), 
            vjust = -0.5, size = 3, 
            position = position_dodge(width = 0.9)) + # Use dodge to align text with bars
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))


p

FileName <- paste(FolderName, "/AccForIronLoss - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```

## Account for iron loss: How?

```{r, echo=F}
q <- data %>% filter(grepl("^AccForIronLoss([1-5]|4A)$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("TRUE", "FALSE", "Yes", "No"))
  ) %>% filter(Response == "Yes" | Response == "TRUE") 


#Faceted by country
p <- ggplot(qdata) + 
  geom_bar(aes(x = Statement, y = Percentage, fill = Country), 
           position = 'dodge', stat = "identity") + 
  # facet_grid(Statement ~ ., 
  #            labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
  #            switch = "y",
  #            scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1],"?"), width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "left") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  #guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = Statement, y = Percentage, label = round(Percentage, 1), group = Country), 
            vjust = -0.5, size = 3, 
            position = position_dodge(width = 0.9)) + # Use dodge to align text with bars
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))


p

FileName <- paste(FolderName, "/AccForIronLossHow - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```

## Concerns Iron Supplements

```{r, echo=F}
q <- data %>% filter(grepl("^ConcernIronSupp([1-9]|5A)$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("TRUE", "FALSE", "Yes", "No"))
  ) %>% filter(Response == "TRUE" | Response == "Yes") 


#Faceted by country
p <- ggplot(qdata) + 
  geom_bar(aes(x = Statement, y = Percentage, fill = Country), 
           position = 'dodge', stat = "identity") + 
  # facet_grid(Statement ~ ., 
  #            labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
  #            switch = "y",
  #            scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1],"?"), width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "left") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  #guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = Statement, y = Percentage, label = round(Percentage, 1), group = Country), 
            vjust = -0.5, size = 3, 
            position = position_dodge(width = 0.9)) + # Use dodge to align text with bars
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))


p

FileName <- paste(FolderName, "/Concerns Iron Supplements - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```
## Reason Supplements

```{r, echo=F}
#Still too much work on this variable homogenization to print it now
# q <- data %>% filter(grepl("^IronSuppSanqReason$", Question)
# 
# 
# qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
#   mutate(
#     #Statement = sub(".*?, then (.*)", "\\1", Question_Text),
#     #Q = "Are the following statements True or False?", #sub("(.*), then.*", "\\1", Question_Text),
#     answer = factor(Response, levels = c("Prefer not to say", "Other", "Non-binary", "Male", "Female" ))
#   )
# 
# #Faceted by country
# p <- ggplot(qdata) + 
#   geom_col(aes(x = Percentage, y = answer, fill = Country)) +  # Swapped x and y
#   facet_wrap(~ Country, strip.position = "top", nrow=1) +  # Use facet_wrap and free_y
#   xlab("Percentage") +  # Label for x-axis (Percentage)
#   ylab(" ") +           # Empty y label
#   ggtitle(unique(qdata$Question_Text)[1]) +
#   scale_x_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120)) +  # Set x scale for Percentage
#   scale_fill_manual(values = country_colors) +
#   guides(fill = FALSE) +
#   theme_bw() +
#   theme(
#     strip.text.y.left = element_text(angle = 0),  # Keeps facet text horizontal
#     strip.placement = "outside",                  # Places facet labels outside
#     strip.text = element_text(size = 12)          # Adjust facet label size for clarity
#   ) +
#   geom_text(aes(x = Percentage, y = answer, label = round(Percentage, 1)), 
#             hjust = -0.5, size = 3) +  # Adjust for horizontal text justification
#   scale_y_discrete(labels = function(x) str_wrap(x, width = 10))  # Set y scale with wrapped text
# 
# p
# 
# FileName <- paste(FolderName, "/Reason supplements - by country.png",sep="")
# ggsave(FileName, width = 10, height = 3)
```

## Iron Def Pref

```{r, echo=F}
q <- data %>% filter(grepl("^IronDefPref[1-9]$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Response = trimws(Response),
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c(1,2,3,4,5))
  )


#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y",
             scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1],"?"),width=75))+
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/Iron Def Pref - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)

```

# Symptoms

## Occurrence

```{r, echo=F}
q <- data %>% filter(grepl("^Symptoms([1-9]|10)$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("Never", "Sometimes", "Often", "Always" ))
  )


#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = Percentage, y = answer, fill = Country)) +  # Swap x and y
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y") +  # Keeps facet labels on the left
  xlab("Percentage") +  # Now label x-axis as "Percentage"
  ylab(" ") +  # Y-axis for "answer"
  ggtitle(paste0(unique(qdata$Q)[1], "?")) +
  scale_x_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "bottom") +  # Ensure x-axis (Percentage) is at the bottom
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0),  # Keeps facet text horizontal
    strip.placement = "outside",  # Places facet labels outside the plot area
    axis.text.y = element_text(hjust = 1),  # Moves y-axis (answer) labels to the right
    axis.title.y = element_text(hjust = 1)  # Adjusts title of y-axis (answer)
  ) +
  geom_text(aes(x = Percentage, y = answer, label = round(Percentage, 1)), 
            hjust = -0.5, size = 3) +  # Adjust text alignment based on new x and y
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10), position="right")  # Adjust y-axis labels (answer)

p

FileName <- paste(FolderName, "/Symptoms - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)

```

## Severity

```{r, echo=F}
q <- data %>% filter(grepl("^Symptoms([1-9]|[1-9][0-9])_Severity$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c(1,2,3,4,5))
  )


#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(unique(qdata$Q)[1])+
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/Symptoms severity - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)

```


# Knowledge

## Blood service

```{r, echo=F}
q <- data %>% filter(grepl("^Knowledge[1-9]$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sub(".*?, then (.*)", "\\1", Question_Text),
    Q = "Are the following statements True or False?", #sub("(.*), then.*", "\\1", Question_Text),
    answer = ordered(Response, levels=c("TRUE", "FALSE", "I don't know"))
  )

#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y",
             scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(unique(qdata$Q)[1])+
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/Knowledge - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```

## Measurement

```{r, echo=F}
q <- data %>% filter(grepl("^Measurement[1-9]$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("Yes", "No", "I don't know"))
  )


#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y",
             scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1], "?"),width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/Measurement - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```

## Knowledge Hb

```{r, echo=F}
q <- data %>% filter(grepl("KnowledgeHb[1-9]$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sub(".*?, then (.*)", "\\1", Question_Text),
    Q = "Are the following statements True or False?", #sub("(.*), then.*", "\\1", Question_Text),
    answer = ordered(Response, levels=c("TRUE", "FALSE", "I don't know"))
  )

#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y",
             scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(unique(qdata$Q)[1])+
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/Knowledge Hb - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```

## Knowledge Ferritin

```{r, echo=F}
q <- data %>% filter(grepl("KnowledgeFer[1-9]$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sub(".*?, then (.*)", "\\1", Question_Text),
    Q = "Are the following statements True or False?", #sub("(.*), then.*", "\\1", Question_Text),
    answer = ordered(Response, levels=c("TRUE", "FALSE", "I don't know"))
  )


#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y",
             scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(unique(qdata$Q)[1])+
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/Knowledge Fer - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```

## Consequence Hb

```{r, echo=F}
q <- data %>% filter(grepl("^ConsequenceHb[1-9]$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("TRUE", "FALSE"))
  )

#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y",
             scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1], "?"),width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/Consequence Hb - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```

## Consequence Fer

```{r, echo=F}
q <- data %>% filter(grepl("^ConsequenceFer[1-9]$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Response = as.character(Response),
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("TRUE", "FALSE")) 
  )%>% 
  filter(as.character(Response) == "TRUE" | as.character(answer) == "FALSE")

#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y",
             scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1], "?"),width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/Consequence Fer - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```

## Iron supplements

```{r, echo=F}
q <- data %>% filter(grepl("^IronSuppKnowledge[1-9]$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Response = as.character(Response),
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("TRUE", "FALSE")) 
  )%>% 
  filter(as.character(Response) == "TRUE" | as.character(answer) == "FALSE")

#Faceted by country
p <- ggplot(qdata) + 
  geom_col(aes(x = answer, y = Percentage, fill = Country)) + 
  facet_grid(Statement ~ Country, 
             labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
             switch = "y",
             scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1], "?"),width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "right") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = answer, y = Percentage, label = round(Percentage, 1)), 
            vjust = -0.5, size = 3) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))

p

FileName <- paste(FolderName, "/Knowledge Iron Supplements - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```

## Iron Supplement Side Effects

```{r, echo=F}
q <- data %>% filter(grepl("^IronSuppSE([1-9])$", Question))

qdata <- merge(q, question_text, by.x = "Question", by.y = "Variable", all.x = TRUE) %>%   
  mutate(
    Statement = sapply(str_split(Question_Text, "[:?]"), function(x) x[2]),
    Statement = ordered(Statement, levels = c(" Restless legs", 
                                              " Dark stool",
                                              " Fatigue",
                                              " Stomach complaints",
                                              " Urge to chew on non-edible products like chalks, ice cubes, pen caps, or raw pasta",
                                              " Headache",
                                              " All of the above",
                                              " None of the above",
                                              " I don't know" )),
    Q = sapply(str_split(Question_Text, "[:?]"), function(x) x[1]),
    answer = ordered(Response, levels=c("TRUE", "FALSE"))
  ) %>% filter(Response == "TRUE") 


#Faceted by country
p <- ggplot(qdata) + 
  geom_bar(aes(x = Statement, y = Percentage, fill = Country), 
           position = 'dodge', stat = "identity") + 
  # facet_grid(Statement ~ ., 
  #            labeller = labeller(Statement = label_wrap_gen(width = 25, multi_line = TRUE)),
  #            switch = "y",
  #            scales= "free_x") + # Moves facet labels to the left
  ylab("Percentage") +
  xlab(" ") +
  ggtitle(str_wrap(paste0(unique(qdata$Q)[1],"?"), width=75)) +
  scale_y_continuous(breaks = seq(0, 100, by = 50), limits = c(0, 120), position = "left") + # Moves y-axis to the right
  scale_fill_manual(values = country_colors) +
  #guides(fill = FALSE) +
  theme_bw() +
  theme(
    strip.text.y.left = element_text(angle = 0), # Keeps facet text horizontal
    strip.placement = "outside"                  # Places labels outside the plot area
  ) +
  geom_text(aes(x = Statement, y = Percentage, label = round(Percentage, 1), group = Country), 
            vjust = -0.5, size = 3, 
            position = position_dodge(width = 0.9)) + # Use dodge to align text with bars
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))


p

FileName <- paste(FolderName, "/Knowledge Iron Supp Side effects - by country.png",sep="")
ggsave(FileName, width = 9, height = 7)
```