---
title: "Donor iron supplement perception data summary FI"
author: "Mikko Arvas"
date: "`r Sys.time()`"
output:
  html_document:
    toc: true
    theme: united
---


TODO:

-summarise all questions

- There is an extra dot in the questions 23 that needs to be removed!

-compare sample to all donors (and/or FinDonors/Biobank) -> put that to another script

-do a version where you remove others than male female (or assign them to male female is possible) -> thats results can be made public and you can make a sex split




```{r setup, include=FALSE}
#echo "rmarkdown::render('summarise_data.Rmd', clean=TRUE,output_format='html_document',output_file='../results/summarise_data.html')" | R --slave
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(gtsummary)
library(likert)
library(sjPlot)
```



```{r}
load("../data/donorironpercep.rdata")
```

# Demographics

## Age

```{r}

p <- ggplot(data %>% filter( `2: What is your gender?` == "Male" | `2: What is your gender?` == "Female"))
p <- p +  geom_histogram(aes(x=`1: What is your age?`),binwidth = 5)
p <- p + facet_wrap(. ~ `2: What is your gender?`)
p

```


Looks quite different from our normal donation population. Make explicit comparison later!


```{r}
data2<- data
colnames(data2) <- str_replace_all(colnames(data2),pattern = " ", "_") %>% 
  str_replace_all(.,".*:_","") %>% 
  str_replace_all(.,"\\?","") %>% 
  str_replace_all(.,",","")

```


```{r}

table2 <-
  tbl_summary(
    data2,
    include = c(
      What_is_your_age,
      In_what_kind_of_area_are_you_do_you_live,
      What_is_the_highest_form_of_education_which_you_have_completed,
      In_general_how_do_you_rate_your_health,
      Do_you_currently_eat_a_vegetarian_or_vegan_diet
      ),
    by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2
```


## Donation history

```{r}
table3 <-
  tbl_summary(
    data2,
    include = c(
      How_many_times_have_you_donated_whole_blood_in_your_lifetime,
      When_was_your_most_recent_donation,
      ),
    by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table3

```



```{r}
#You do no need to add row breaks to questions if you just replace  "_" with " "
# findmid <- function(x,sep="_") {
#   z <- str_locate_all(x, sep)
#     z <- z[[1]][,"start"]
#   zno <- z[ceiling(length(z)/2)] 
#   z1 <- str_sub(x,start = 1L, end=zno - 1)
#   z2 <- str_sub(x,start = zno, end=-1L)
#   z <- str_c(z1,"\n",z2)
#   z
# }

```


# Blood service conduct


```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^10\\.\\d"))) #%>% 
#    mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 5
```


```{r , warning=FALSE}
q10 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q10, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


# Donation symptoms



```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^11\\.\\d"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 4

levels(data$`11.1: Bruises at the location where the needle was inserted`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


# Donation symptoms - severity


```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^12\\.\\d"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 6

levels(data$`12.10: Please indicate the severity of the symptoms? Thirst`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

# Donation knowledge

## Donation general knowledge



```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^13\\.\\d"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`13.1: During each donation, a donor gives approximately 500ml (16 oz.) of blood`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```




```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^14\\.\\d"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`14.1: During each donation, a donor gives approximately 500ml (16 oz.) of blood`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```



## Donation hemoglobin knowledge



```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^15\\.\\d"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`15.2: Hemoglobin transports oxygen through the body`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```




```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^16\\.\\d"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`16.2: Hemoglobin transports oxygen through the body`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```





## Donation ferritin knowledge



```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^17\\.\\d"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`17.1: Iron is needed for the production of hemoglobin in the body`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```




```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^18\\.\\d"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`18.1: Iron is needed for the production of hemoglobin in the body`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


## Donation knowledge measurments

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^19\\.\\d"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`19.1: Are any of the following blood values measured by FRCBS before, during or after donation? Hemoglobin (Hb)`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```



## Donation knowledge process


```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^20"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`20: What happens if a donor has a low hemoglobin value prior to donating? Hemoglobin is not measured`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

# Have you ever been deferred


```{r}
table2 <-
  tbl_summary(
    data2,
    include = c(
      Have_you_ever_been_deferred_or_ineligible_to_donate_due_to_low_hemoglobin
      ),
    by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2

```

## When was the last deferral

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^22"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`22: When was your last deferral? 1-2 years ago`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


## Was the information about deferral ...

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^23"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 5

levels(data$`23.1: Was the information you received about your deferral from the blood service: Understandable`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

# Missing information

```{r}

table2 <-
  tbl_summary(
    data2,
    include = c(
      Which_information_was_missing_from_the_information_you_received_about_your_deferral_from_the_blood_service
            ),
    by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2


```


## Motivation

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^25|^26"))) #%>% 
    #mutate_all( ~ as.numeric(.x))

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 5

levels(data$`26: If you would be deferred due to low hemoglobin, what effect would this have on your motivation to continue to donate?`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

# Iron deficiency 

## Symptoms

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^27"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`27: Do you know what possible symptoms of iron deficiency (a lack of iron in the body) are? Dark stool`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```




```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^27"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`27: Do you know what possible symptoms of iron deficiency (a lack of iron in the body) are? Dark stool`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

## Replacement



```{r}

table2 <-
  tbl_summary(
    data2,
    include = c(
      When_you_donate_blood_you_lose_some_iron_as_well_do_you_do_anything_before_you_donate_to_help_to_manage_any_iron_lose,
      How_do_you_take_the_amount_of_iron_you_lose_during_a_donation_into_account
            ),
    by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2


```

## Information

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^30"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 2

levels(data$`27: Do you know what possible symptoms of iron deficiency (a lack of iron in the body) are? Dark stool`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


# Opinion on supplements

## Iron

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^32"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )
#colnames(items) <- unlist(lapply(colnames(items),FUN = findmid,sep=" "))

nlevels = 5

levels(data$`32.1: What is your opinion on the use of iron supplements? Bad (1) -  Good (5)`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

## Dietary


```{r}
table2 <-
  tbl_summary(
    data2,
    include = c(
      Do_you_take_dietary_supplements_containing_vitamin_D,
      Do_you_take_other_dietary_supplements
            ),
    by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2

```




```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^35"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`35.1: Why did/do you take dietary supplements? It was advised by a professional`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


```{r}
 table(      data2$`Is_there_a_different_reason_why_you_use(d)_dietary_supplements`)
```

## Iron supplements statements

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^38"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`38.1: Are the following statements about iron supplements true or false? Iron supplements are provided by the blood service to donors with reduced iron levels`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^39"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`39.1: Are the following statements about iron supplements true or false? confidence Iron supplements are provided by the blood service to donors with reduced iron levels`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


## Iron supplement side effects


```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^40"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 2

levels(data$`39.1: Are the following statements about iron supplements true or false? confidence Iron supplements are provided by the blood service to donors with reduced iron levels`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```

## Use

```{r}

table2 <-
  tbl_summary(
    data2,
    include = c(
      Have_you_ever_taken_or_are_you_currently_taking_iron_supplements
            ),
    by = What_is_your_gender, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_n()  # add column with total number of non-missing observations
table2


```



```{r , warning=FALSE}
items = data2 %>% 
    select(which(str_detect(colnames(data) ,"^42"))) 

colnames(items) <- str_replace_all(string = colnames(items),pattern = "_",replacement = " " )

nlevels = 3

levels(data$`42.1: What experiences do you have with iron supplements? Physical fitness`)

```


```{r , warning=FALSE}
q11 <- likert(
  items = as.data.frame(items),
  nlevels = nlevels
  
)
plot(q11, 
     type = "heat",
     legend.position = "bottom",
     text.size=3,
     include.histogram = FALSE)
```


