---
title: "Donor iron supplement perception study data description and translation - Finland"
author: "Mikko Arvas"
date: "`r Sys.time()`"
output:
  html_document:
    df_print: paged
  pdf_document:
    fig_caption: yes
    number_sections: yes
---

\tableofcontents


```{r setup, include=FALSE}

  
library(knitr)
opts_chunk$set(#results = 'asis',      # Can also be set at the chunk-level. IT IS NEEDED IN THE dfsummary chunck
               comment = NA,
               prompt  = FALSE,
               cache   = FALSE,
               echo = TRUE,
               message = FALSE,
               warning = FALSE,
               width.cutoff=60
)
library(summarytools)
st_options(plain.ascii = FALSE,        # Always use this option in Rmd documents
           style        = "rmarkdown", # Always use this option in Rmd documents
           footnote     = NA,          # Makes html-rendered results more concise
           subtitle.emphasis = FALSE)  # Improves layout with some rmardown themes
library(tidyverse)
library(readxl)
library(lubridate)
library(summarytools)

```


# Read and summarise data


```{r}
data <- read_excel("../data/Kopio_Kyselytutkimusverenluovuttajille-5067333.xlsx")
colnames(data)
```


# Translate questions



# Translate answers




## Mapping functions 

```{r}
#

#col 11 and 12 

f1 <- function (x){
  x <- fct_recode(x,  
                  "Disagree" = "2",
                  "Neutral"="3",
                  "Agree"="4",
                  "Totally disagree" =  "1",
                  "Totally disagree" =  "1",
                  "Totally agree" = "5"
  )
  x <- factor(
    x,
    levels = c("Totally disagree","Disagree","Neutral","Agree","Totally agree"),
    ordered = TRUE
  )
  x
}

f2 <- function (x){
  x <- fct_recode(x,  
                  "Never" = "something_in_some_language",
                  "Sometimes" = "something_in_some_language",
                  "Often" = "something_in_some_language",
                  "Always" = "Aina"
  )
  x <- factor(
    x,
    levels = c("Never","Sometimes","Often","Always"),
    ordered = TRUE
  )
  x  
}

f3 <- function (x){
  x <- fct_recode(x,  
                  "1" = "1",
                  "5" = "5"
                  )
  x <- factor(
    x,
    levels=c("1","2","3","4","5","6"),
    ordered = TRUE
  )
  x
}

f4 <- function (x){
  x <- fct_recode(x,
                  "FALSE" = "something_in_some_language",
                  "TRUE" = "something_in_some_language"
                  
                  )
  x <- factor(
    x,
    levels=c("FALSE","TRUE"),
  )
  x
}

f5 <- function (x){
  x <- fct_relevel(
    x,
    "50/50",
    "100%"
  )
x <- factor(
    x,
    levels=c("50/50","100%"),
    ordered = TRUE
  )
  x
}


f6 <- function (x){
  x <- fct_recode(x,
                  "No" = "something_in_some_language",
                  "Yes" = "something_in_some_language"
                  
                  )
  x <- factor(
    x,
    levels=c("No","Yes"),
  )
  x
}


f7 <- function (x){
  x <- as.character(x)
  x <- fct_recode(x,  
                  "FALSE" = "0",
                  "TRUE" = "1"
                  )
  x <- factor(
    x,
    levels=c("FALSE","TRUE"),
  )
  x
}

f8 <- function (x){
  x <- fct_recode(x,  
                  "Increased" = "something_in_some_language",
                  "No effect" = "something_in_some_language",
                  "Decreased" = "something_in_some_language"
  )
  x <- factor(
    x,
    levels=c("Increased","No effect","Decreased"),
  )
  x
}

f9 <- function (x){
  x <- fct_recode(x,
                  "Agree" = "something_in_some_language",
                  "Disagree" = "something_in_some_language"
                  
                  )
  x <- factor(
    x,
    levels=c("Agree","Disagree"),
  )
  x
}

f10 <- function (x){
  x <- factor(
    x,
    levels=c("1","2","3","4","5","6"),
    ordered = TRUE
  )
  x
}

f11 <- function (x){
  x <- factor(
    x,
    levels=c("1","2","3","4","5"),
    ordered = TRUE
  )
  x
}


```


## Main processing

```{r}

# Columns containing just yes and no
yesandnocols <- data %>% head(n=1) %>% mutate_all(~str_detect(.,"^No_in_some_language$")) %>% 
  bind_rows(
data %>% head(n=1) %>% mutate_all(~str_detect(.,"^yes_in_some_language$")) ) %>% 
  summarise(across(everything(), ~ any(.x)))

#Columns containing just 0 or 1
zero1cols <- data %>%  
  summarise(across(everything(), ~ str_c(names(table(.x)),collapse="") == "01"))

#Columns containing just 1-5
cols12345 <- data %>% summarise(across(everything(), ~ str_c(names(table(.x)),collapse="") == "12345"))
cols1345 <- data %>% summarise(across(everything(), ~ str_c(names(table(.x)),collapse="") == "1345"))
cols2345 <- data %>% summarise(across(everything(), ~ str_c(names(table(.x)),collapse="") == "2345"))

cols12345 <- bind_rows(cols12345,
                       cols1345,
                       cols2345) %>%  
  summarise(across(everything(), ~ any(.x))) & !str_detect(colnames(data) ,"^49\\.\\d")
#49 has scale from 1-6. But if there are no 6s then it is detected here and ruins things later



tmp <- data %>% 
  mutate(`something_in_some_language` = as.Date(`something_in_some_language`)) %>% 
  mutate( `1.0: something_in_some_language` = as.numeric(`1.0: something_in_some_language`)  ) %>%
  #here a set of questions is detected with some regular expression and then one of the
  #processing functions above is applied to process those questions
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f1(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f2(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f3(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f4(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f5(.) ) %>%
  #here instead of a regular expression, above a vector is made which tells which columns to process
  mutate_at(vars(which(as.logical(yesandnocols))), ~ f6(.) ) %>%
  mutate_at(vars(which(as.logical(zero1cols))), ~ f7(.) ) %>%
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f8(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f9(.) ) %>%
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f10(.) ) %>%
  mutate_at(vars(which(cols12345)), ~ f11(.) ) %>%
  mutate(
    `2: something_in_some_language` =  fct_recode(`2: something_in_some_language`,  
                  "Male" = "something_in_some_language",
                  "Female" = "something_in_some_language",
                  "Non-binary" = "something_in_some_language",
                  "Prefer not to say" = "something_in_some_language"
                  ),
    `3: something_in_some_language?` = fct_recode(`3: something_in_some_language`,  
    "Yes" = "something_in_some_language",
    "No, due to current pregnancy" = "something_in_some_language",
    "No, due to menopause" = "something_in_some_language",
    "No, due to current contraception use" = "something_in_some_language"
     ),  
    
    `4: something_in_some_language` = fct_recode(`4: something_in_some_language?`,
                     "In a city of over 100,000 people" = "something_in_some_language",
                    "In a town of less than 100,000 people, or in the countryside" = "something_in_some_language"
                                                 
    ),
      `5: something_in_some_language?` =fct_recode(`5: something_in_some_language?`,
"None" = "something_in_some_language",
"Primary school" = "something_in_some_language", 
"High school" = "something_in_some_language",
"College" = "something_in_some_language",
"University" = "something_in_some_language",
      ) %>% fct_relevel(
        "None",
"Primary school", 
"High school",
"College",
"University"
      ) %>% as.ordered(.)
,
    `6: something_in_some_language` = fct_recode(    `6: something_in_some_language`,
"Excellent" =  "something_in_some_language",
"Very good" =  "something_in_some_language",
"Good" =   "something_in_some_language",
"Fair" =  "something_in_some_language",
"Poor" =  "Huono"
) %>% fct_relevel(.,
"Poor",
"Fair",
"Good",
"Very good",
"Excellent",  
) %>% as.ordered(.)
,
    `7: something_in_some_language` =
  str_replace_all(data$`7: something_in_some_language`,"\\(|\\)","_") %>% 
    fct_recode(.,
      "Yes, vegan (no animal products)" =  "something_in_some_language",
"Yes, vegetarian (no meat and no fish)" =  "something_in_some_language",
"Yes, pescatarian (no meat)" =  "something_in_some_language",
"Yes, flexitarian (at least three days without meat)" = "something_in_some_language" ,
"Yes, lakto-ovovegan (no meat and no fish, but milk and eggs)" = "something_in_some_language",
"No" = "something_in_some_language"

    ),    
    `8: something_in_some_language` = fct_recode(`8: something_in_some_language`,
      "1 - 3 times" = "something_in_some_language",
"4 - 10 times" = "something_in_some_language",
"More than 10 times" = "something_in_some_language",
"None" = "something_in_some_language"
    ) %>% fct_relevel(.,
    "None",
    "1 - 3 times",
"4 - 10 times",
"More than 10 times"
) %>% as.ordered(.)
,
    `9: something_in_some_language` = fct_recode(`9: something_in_some_language`,
"Within the last 6 months" =  "something_in_some_language",
"6 months to a year ago" =  "something_in_some_language",
"1-2 years ago" =  "something_in_some_language",
"I cannot remember" = "something_in_some_language",
    ) %>% fct_relevel(.,
"Within the last 6 months",
"6 months to a year ago",
"1-2 years ago",
"I cannot remember"
                      ) %>% as.ordered(.)

,
`21: something_in_some_language`
=fct_recode(`21: something_in_some_language`,
            "No" = "something_in_some_language",
            "I don’t know"= "something_in_some_language",
            "Yes, once "= "something_in_some_language",
            "Yes, multiple times "= "something_in_some_language"
            
),

`29: something_in_some_language` = 
  fct_recode(`29: something_in_some_language`,
             "I take iron supplements acquired by myself"    = "something_in_some_language",
             "I take multivitamins that contain iron "   = "something_in_some_language",
             "I take iron supplements provided by the blood service"  = "something_in_some_language",
             "I take iron supplements acquired by myself"  = "something_in_some_language",
             "I eat more iron-rich foods"    = "something_in_some_language",
             "I take iron supplements acquired by myself"   = "something_in_some_language"
  ),        
`34: something_in_some_language` =
  fct_recode(`34: something_in_some_language`,
             "Never" = "something_in_some_language",
             "Not anymore" =  "something_in_some_language",
             "Sometimes" =  "something_in_some_language",
             "Every day" =  "something_in_some_language"
  ),
`41: something_in_some_language` =
  fct_recode(`41: something_in_some_language`,
             "No, I have never taken iron (containing) supplements " = "something_in_some_language",
             "Yes, I am currently taking iron supplements ordered to me by a doctor"    = "something_in_some_language",
             "Yes, I am currently taking iron supplements from a drugstore"   =  "something_in_some_language",
             "Yes, I am currently taking iron supplements provided to me by the blood service" = "something_in_some_language", 
             "Yes, I take multivitamins that contain iron "  =  "something_in_some_language", 
             "I am taking multivitamins, but I do not know whether or not they contain iron" = "something_in_some_language",
             "I have taken iron supplements/multivitamins before, but not anymore "      = "something_in_some_language" 
             
  ),



  )
  
```


# Deal with open text answers

## 3: something_in_some_language

```{r}
tmp %>% count(`3: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


```{r}


tmp <- tmp %>%  
  mutate(
    `something_in_some_language` = str_remove_all(`something_in_some_language`,"\""), # there we some extra '\' that needed to be removed
  `3: something_in_some_language` = fct_recode(`3: something_in_some_language`,
 "No, other" =              "something_in_some_language",
 "No, other" =              "something_in_some_language",
 #... maybe some other alternative open text answers
  "No, due to menopause" =  "something_in_some_language",
# ...
   "No, due to current contraception use"  =           "something_in_some_language",
#... 
  "No, due to hysterectomy" =             "something_in_some_language",
"No, due to menopause"    =           "something_in_some_language",
  "No, other" =             "something_in_some_language",

)
)

tmp %>% count(`3: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)


```


## 5: Mikä on korkein suorittamasi koulutusaste?


```{r}
tmp %>% count(`5: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)


```

```{r}
tmp <- tmp %>% mutate(
  `5: something_in_some_language` =fct_recode(`5: something_in_some_language`,
 "High school" = "something_in_some_language",
# ... maybe some other alternatives
 "Primary school" = "something_in_some_language",
"High school" ="something_in_some_language",
"College" ="something_in_some_language",
"University" = "something_in_some_language"
),
 `5: something_in_some_language` = fct_relevel(
    `5: something_in_some_language`,
    "Primary school",
    "High school",
    "College",
    "University"
  ),
  `5: something_in_some_language` = as.ordered(
    `5: something_in_some_language`)
)

tmp %>% count(`5: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


## 24: Mistä olisit halunnut lisätietoja?


```{r}
tmp %>% count(`24: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```




```{r}
tmp <- tmp %>% mutate(
`24: something_in_some_language` = 
  fct_recode(`24: something_in_some_language`,
    "Other"= "something_in_some_language", 
    "Iron stores/ferritin" = "something_in_some_language", 
    "Other" = "something_in_some_language", 
    "Information on the consequences of low hemoglobin levels" = "something_in_some_language", 
    "Information on how to restore hemoglobin levels" = "something_in_some_language", 
    "Information on what hemoglobin is" = "something_in_some_language", 
   "No information was missing" =  "something_in_some_language" 

  ),
)

```


```{r}
tmp %>% count(`24: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


## 36: Onko olemassa jokin muu syy, miksi käytät tai olet käyttänyt ravintolisiä?`


```{r}
tmp %>% count(`36: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```



```{r}
tmp <- tmp %>% mutate(
  `36: something_in_some_language` =
    case_when(
      !is.na(`36: something_in_some_language`) & 
        `36: something_in_some_language` != "No" ~ "Other",
      TRUE ~ `36: something_in_some_language`
          ),        
   `36: something_in_some_language` = 
    as_factor(`36: something_in_some_language`)    

)
```


```{r}
tmp %>% count(`36: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


## 44: Askarruttaako jokin muu rautalisiin liittyvä asia sinua?


```{r}
tmp %>% count(`44: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)

```


```{r}
tmp <- tmp %>% mutate(
  `44: something_in_some_language` =
    case_when(
      !is.na(`44: something_in_some_language`) & 
        `44: something_in_some_language` != "No" ~ "Other",
      TRUE ~ `44: something_in_some_language`
          ),        
   `44: something_in_some_language` = 
    as_factor(`44: something_in_some_language`)
)
```


```{r}
tmp %>% count(`44: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```

## 46: Mikä on sinulle tärkein syy ottaa vastaan Veripalvelun tarjoama rautalisä?


```{r}
tmp %>% count(`46: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


```{r}
tmp <- tmp %>% mutate(
  `46: something_in_some_language` =
    fct_recode(`46: something_in_some_language`,
               "To improve my health" = "something_in_some_language",
               # ... maybe some alternative ansers
               "To be able to donate without delays" = "something_in_some_language",
               "I would never take them" = "something_in_some_language" ,
               "To improve my health" = "something_in_some_language",
               "Other" = "something_in_some_language",
               "Other" = "something_in_some_language",
               "To recover from donation" = "something_in_some_language"
    )
)


```



```{r}
tmp %>% count(`46: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


## Removed open texts

### 37.1: Voisitko harkita ravintolisien käyttöä?: Kyllä, koska

```{r}
tmp %>% count(`37.1: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


### 37.2: Voisitko harkita ravintolisien käyttöä?: En, koska

```{r}
tmp %>% count(`37.2: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
 
```


```{r}

```




```{r}
summary(tmp)
```




## Translate questions

```{r}

questions <- read_excel("../data/Tulokset - Donor Perception Survey question translations (ID 125823).xlsx")
questions <- questions %>% 
  mutate(
    QuestionWNo = str_c(str_extract(Kysymys, "^.*\\d+\\:")," ",Question) %>% str_replace("\\.0\\:",":") %>% 
      str_replace("\\.$","") %>% str_replace_all("\\.\\:",":") 
  )


```


```{r}
data <- tmp %>% select(-`Päivämäärä`)
colnames(data) <- questions$QuestionWNo

#Remove 37.1 and 37.2
data <- data %>% 
  select(-(which(str_detect(colnames(data) ,"^37\\.\\d"))))

save(data,file="../results/donorironpercep.rdata")
```


# Export summary data

NB. this has not been tested it is just an example

```{r}

#Read in some xslx containing all the questions and their abbreviations
questions_with_abbr_tmp <- read_excel("../data/Kopio_DPS Variable Overview.xlsx")

#Filter the questions so that they correspond to your countries data
questions_with_abbr <- questions_with_abbr_tmp %>%  filter(!is.na(Finland))

```





```{r}
#tmp should be your final data object after all the questions processing
datawabbr <- tmp %>% 
  #Remove Date from data 
  select(-`Date`) %>% 
  #Remove some unwanted questions
  select(-(which(str_detect(colnames(tmp) ,"^37\\.\\d"))))

#Name the questions from the abbreviations from xlsx if you are absolute sure that
#they match. If you have done this earlier you don't need to do it now.
colnames(datawabbr) <- questions_with_abbr$`Variable name`


#Remove again some unwanted questions
datawabbr <- datawabbr %>% select(-SupplementsOpen1,-SupplementsOpen2)

#Save data
save(datawabbr,file="../results/donorironpercepwabbr.rdata")


```


```{r}
#cut age for summarisation
datawabbr$Age <- cut(datawabbr$Age,breaks=c(min(datawabbr$Age),seq(from=25,to=65,by=10),max(datawabbr$Age)),include.lowest = TRUE)
datawabbr$Age <- factor(datawabbr$Age,ordered = TRUE)

```



```{r}
#Export summary count data
sumlistfi <- apply(datawabbr,MARGIN = 2,FUN = table)
saveRDS(sumlistfi,file="../results/countfi.RDS")

```


```{r}
#Summarise column classes
colclasses <- data %>% ungroup %>% summarise(across(everything(), ~ class(.x))) %>% t() %>% as_tibble(rownames="col")

colclasses %>% count(V1)

```




```{r}
#Summarise column data levels
fnlab <- function(x){
  paste(names(table(x)),collapse = "/")
} 

fnlev <- function(x){
  paste(levels(x),collapse = "/")
} 

all_labels <- datawabbr %>% summarise_all(
  ~fnlab(.)
  
)
all_levels <- datawabbr %>% summarise_all(
  ~fnlev(.)
)

levs_and_labs <- bind_cols(labs=t(all_levels),levs=t(all_labels))
 
levs_and_labs$col <- colnames(all_levels)

questions_with_abbr_out <-    full_join(
  questions_with_abbr_tmp,
  colclasses,
  by = c("Variable name"="col")
) %>% 
  full_join(
    levs_and_labs,
    by = c("Variable name"="col")
  )


openxlsx::write.xlsx(
  questions_with_abbr_out,
       file="../results/questions_classes.xlsx"
)

```







# Summarise 


```{r}
dfSummary(data,
          plain.ascii = FALSE, 
          style = "grid", 
          graph.col = TRUE,
          graph.magnif = 0.75, 
          valid.col = FALSE, 
          tmp.img.dir = "/tmp")


```



