---
title: "Donor iron supplement perception study data description and translation - Finland"
author: "Mikko Arvas"
date: "`r Sys.time()`"
output:
  html_document:
    df_print: paged
  pdf_document: 
    fig_caption: yes
    number_sections: yes
---

\tableofcontents


```{r setup, include=FALSE}

  
library(knitr)
opts_chunk$set(#results = 'asis',      # Can also be set at the chunk-level. IT IS NEEDED IN THE dfsummary chunck
               comment = NA,
               prompt  = FALSE,
               cache   = FALSE,
               echo = TRUE,
               message = FALSE,
               warning = FALSE,
               width.cutoff=60
)
library(summarytools)
st_options(plain.ascii = FALSE,        # Always use this option in Rmd documents
           style        = "rmarkdown", # Always use this option in Rmd documents
           footnote     = NA,          # Makes html-rendered results more concise
           subtitle.emphasis = FALSE)  # Improves layout with some rmardown themes
library(tidyverse)
library(readxl)
library(lubridate)
library(summarytools)

```


# Read and summarise data


```{r}
# Open SPSS dataset with survey data
Data <- read_sav("L:/DonorMedicin/FORTE/E Internation Donor Perception Survey/A Source documents/iDPS - NL/Donor Perceptie IJzersupplementen.sav")
data <- Data
colnames(data)
```


# Translate questions
```{r}
# Delete unused variables
data <- subset(data, select = -c(StartDate, EndDate, Status, Duration__in_seconds_, RecordedDate, ResponseId, DistributionChannel, UserLanguage))


names(data) <- gsub("^Q3$", "Age", names(data))
names(data) <- gsub("^Q8$", "Sex", names(data))
names(data) <- gsub("^Q8_4_TEXT$", "Sex_other", names(data))
names(data) <- gsub("^Q9$", "Menstruation", names(data))
names(data) <- gsub("^Q9_5_TEXT$", "Menstruation_other", names(data))
names(data) <- gsub("^Q11$", "Area", names(data))
names(data) <- gsub("^Q12$", "Education", names(data))
names(data) <- gsub("^Q12_7_TEXT$", "Education_other", names(data))
names(data) <- gsub("^Q13$", "Health", names(data))
names(data) <- gsub("^Q15$", "Diet", names(data))
names(data) <- gsub("^Q16$", "Number_donation", names(data))
names(data) <- gsub("^Q74$", "Last_donation", names(data))
names(data) <- gsub("^Q92$", "Location_donation", names(data))

names(data) <- gsub("^Q45_1$", "OpinionBloodService1", names(data))
names(data) <- gsub("^Q45_2$", "OpinionBloodService2", names(data))
names(data) <- gsub("^Q45_3$", "OpinionBloodService3", names(data))
names(data) <- gsub("^Q45_4$", "OpinionBloodService4", names(data))
names(data) <- gsub("^Q45_5$", "OpinionBloodService5", names(data))
names(data) <- gsub("^Q45_6$", "OpinionBloodService6", names(data))
names(data) <- gsub("^Q45_7$", "OpinionBloodService7", names(data))
names(data) <- gsub("^Q45_8$", "OpinionBloodService8", names(data))

names(data) <- gsub("^Q19_1$", "Symptoms1", names(data))
names(data) <- gsub("^Q19_2$", "Symptoms2", names(data))
names(data) <- gsub("^Q19_3$", "Symptoms3", names(data))
names(data) <- gsub("^Q19_4$", "Symptoms4", names(data))
names(data) <- gsub("^Q19_5$", "Symptoms5", names(data))
names(data) <- gsub("^Q19_6$", "Symptoms6", names(data))

names(data) <- gsub("^Q82_1$", "Symptoms1_Severity", names(data))
names(data) <- gsub("^Q82_2$", "Symptoms2_Severity", names(data))
names(data) <- gsub("^Q82_3$", "Symptoms3_Severity", names(data))
names(data) <- gsub("^Q82_4$", "Symptoms4_Severity", names(data))
names(data) <- gsub("^Q82_5$", "Symptoms5_Severity", names(data))
names(data) <- gsub("^Q82_6$", "Symptoms6_Severity", names(data))

names(data) <- gsub("^Q21_1$", "Knowledge1", names(data))
names(data) <- gsub("^Q21_2$", "Knowledge2", names(data))
names(data) <- gsub("^Q21_3$", "Knowledge3", names(data))
names(data) <- gsub("^Q21_4$", "Knowledge4", names(data))

names(data) <- gsub("^Q83_1$", "Knowledge1_Certainty", names(data))
names(data) <- gsub("^Q83_2$", "Knowledge2_Certainty", names(data))
names(data) <- gsub("^Q83_3$", "Knowledge3_Certainty", names(data))
names(data) <- gsub("^Q83_4$", "Knowledge4_Certainty", names(data))

names(data) <- gsub("^Q22_1$", "KnowledgeHb1", names(data))
names(data) <- gsub("^Q22_2$", "KnowledgeHb2", names(data))
names(data) <- gsub("^Q22_3$", "KnowledgeHb3", names(data))
names(data) <- gsub("^Q22_4$", "KnowledgeHb4", names(data))
names(data) <- gsub("^Q84_1$", "KnowledgeHb1_Certainty", names(data))
names(data) <- gsub("^Q84_2$", "KnowledgeHb2_Certainty", names(data))
names(data) <- gsub("^Q84_3$", "KnowledgeHb3_Certainty", names(data))
names(data) <- gsub("^Q84_4$", "KnowledgeHb4_Certainty", names(data))

names(data) <- gsub("^Q51_1$", "KnowledgeFer1", names(data))
names(data) <- gsub("^Q51_2$", "KnowledgeFer2", names(data))
names(data) <- gsub("^Q51_3$", "KnowledgeFer3", names(data))
names(data) <- gsub("^Q51_4$", "KnowledgeFer4", names(data))
names(data) <- gsub("^Q85_1$", "KnowledgeFer1_Certainty", names(data))
names(data) <- gsub("^Q85_2$", "KnowledgeFer2_Certainty", names(data))
names(data) <- gsub("^Q85_3$", "KnowledgeFer3_Certainty", names(data))
names(data) <- gsub("^Q85_4$", "KnowledgeFer4_Certainty", names(data))

names(data) <- gsub("^Q55_1$", "Measurement1", names(data))
names(data) <- gsub("^Q55_2$", "Measurement2", names(data))
names(data) <- gsub("^Q55_3$", "Measurement3", names(data))
names(data) <- gsub("^Q55_4$", "Measurement4", names(data))
names(data) <- gsub("^Q55_5$", "Measurement5", names(data))

names(data) <- gsub("^Q57_1$", "ConsequenceHb1", names(data))
names(data) <- gsub("^Q57_2$", "ConsequenceHb2", names(data))
names(data) <- gsub("^Q57_3$", "ConsequenceHb3", names(data))
names(data) <- gsub("^Q57_4$", "ConsequenceHb4", names(data))
names(data) <- gsub("^Q57_5$", "ConsequenceHb5", names(data))
names(data) <- gsub("^Q57_6$", "ConsequenceHb6", names(data))
names(data) <- gsub("^Q57_7$", "ConsequenceHb7", names(data))

names(data) <- gsub("^Q59_1$", "ConsequenceFer1", names(data))
names(data) <- gsub("^Q59_2$", "ConsequenceFer2", names(data))
names(data) <- gsub("^Q59_3$", "ConsequenceFer3", names(data))
names(data) <- gsub("^Q59_4$", "ConsequenceFer4", names(data))
names(data) <- gsub("^Q59_5$", "ConsequenceFer5", names(data))
names(data) <- gsub("^Q59_6$", "ConsequenceFer6", names(data))
names(data) <- gsub("^Q59_7$", "ConsequenceFer7", names(data))

names(data) <- gsub("^Q62$", "Deferral", names(data))
names(data) <- gsub("^Q76$", "Last_Deferral", names(data))
names(data) <- gsub("^Q64_1$", "DeferralInfo1", names(data))
names(data) <- gsub("^Q64_2$", "DeferralInfo2", names(data))
names(data) <- gsub("^Q64_3$", "DeferralInfo3", names(data))
names(data) <- gsub("^Q64_4$", "DeferralInfo4", names(data))
names(data) <- gsub("^Q64_5$", "DeferralInfo5", names(data))
names(data) <- gsub("^Q69_1$", "LackDeferralInfo1", names(data))
names(data) <- gsub("^Q69_2$", "LackDeferralInfo2", names(data))
names(data) <- gsub("^Q69_3$", "LackDeferralInfo3", names(data))
names(data) <- gsub("^Q69_4$", "LackDeferralInfo4", names(data))
names(data) <- gsub("^Q69_4_TEXT$", "LackDeferralInfoTEXT", names(data))

names(data) <- gsub("^Q71_1$", "Deferral_Motivation1", names(data))
names(data) <- gsub("^Q73_1$", "Deferral_Motivation2", names(data))
names(data) <- gsub("^Q42_1$", "SymptomsID1", names(data))
names(data) <- gsub("^Q42_2$", "SymptomsID2", names(data))
names(data) <- gsub("^Q42_3$", "SymptomsID3", names(data))
names(data) <- gsub("^Q42_4$", "SymptomsID4", names(data))
names(data) <- gsub("^Q42_5$", "SymptomsID5", names(data))
names(data) <- gsub("^Q42_6$", "SymptomsID6", names(data))
names(data) <- gsub("^Q42_7$", "SymptomsID7", names(data))
names(data) <- gsub("^Q42_8$", "SymptomsID8", names(data))
names(data) <- gsub("^Q42_9$", "SymptomsID9", names(data))

names(data) <- gsub("^Q49$", "AccForIronLoss", names(data))
names(data) <- gsub("^Q51_1.0$", "AccForIronLoss1", names(data))
names(data) <- gsub("^Q51_4.0$", "AccForIronLoss2", names(data))
names(data) <- gsub("^Q51_2.0$", "AccForIronLoss3", names(data))
names(data) <- gsub("^Q51_3.0$", "AccForIronLoss4A", names(data))
names(data) <- gsub("^Q51_3_TEXT$", "AccForIronLoss4B", names(data))
names(data) <- gsub("^Q53_1$", "DeferralSource1", names(data))
names(data) <- gsub("^Q53_2$", "DeferralSource2", names(data))
names(data) <- gsub("^Q53_3$", "DeferralSource3", names(data))
names(data) <- gsub("^Q53_4$", "DeferralSource4", names(data))
names(data) <- gsub("^Q53_5$", "DeferralSource5", names(data))
names(data) <- gsub("^Q88$", "DeferralSource6A", names(data))
names(data) <- gsub("^Q88_1_TEXT$", "DeferralSource6B", names(data))

names(data) <- gsub("^Q62_1$", "Supplements1", names(data))
names(data) <- gsub("^Q62_2$", "Supplements2", names(data))
names(data) <- gsub("^Q62_3$", "Supplements3", names(data))
names(data) <- gsub("^Q62_4$", "Supplements4", names(data))
names(data) <- gsub("^Q73_1.0$", "SupplementsUse", names(data))
names(data) <- gsub("^Q73_2$", "SupplementsUse1A", names(data))
names(data) <- gsub("^Q73_3$", "SupplementsUse2A", names(data))
names(data) <- gsub("^Q73_1_TEXT$", "SupplementsUse3A", names(data))
names(data) <- gsub("^Q73_2_TEXT$", "SupplementsUse1B", names(data))
names(data) <- gsub("^Q73_3_TEXT$", "SupplementsUse2B", names(data))

names(data) <- gsub("^Q34$", "SupplementsOpen", names(data))
names(data) <- gsub("^Q34_1_TEXT$", "SupplementsOpen1", names(data))
names(data) <- gsub("^Q34_2_TEXT$", "SupplementsOpen2", names(data))

names(data) <- gsub("^Q36_1$", "IronSuppKnowledge1", names(data))
names(data) <- gsub("^Q36_2$", "IronSuppKnowledge2", names(data))
names(data) <- gsub("^Q36_3$", "IronSuppKnowledge3", names(data))
names(data) <- gsub("^Q36_4$", "IronSuppKnowledge4", names(data))
names(data) <- gsub("^Q90_1$", "IronSuppKnowledge1_Certainty", names(data))
names(data) <- gsub("^Q90_2$", "IronSuppKnowledge2_Certainty", names(data))
names(data) <- gsub("^Q90_3$", "IronSuppKnowledge3_Certainty", names(data))
names(data) <- gsub("^Q90_4$", "IronSuppKnowledge4_Certainty", names(data))

names(data) <- gsub("^Q37_1$", "IronSuppSE1", names(data))
names(data) <- gsub("^Q37_2$", "IronSuppSE2", names(data))
names(data) <- gsub("^Q37_3$", "IronSuppSE3", names(data))
names(data) <- gsub("^Q37_4$", "IronSuppSE4", names(data))
names(data) <- gsub("^Q37_5$", "IronSuppSE5", names(data))
names(data) <- gsub("^Q37_6$", "IronSuppSE6", names(data))
names(data) <- gsub("^Q37_7$", "IronSuppSE7", names(data))
names(data) <- gsub("^Q37_8$", "IronSuppSE8", names(data))
names(data) <- gsub("^Q37_9$", "IronSuppSE9", names(data))

names(data) <- gsub("^Q38$", "IronSuppUse", names(data))
names(data) <- gsub("^Q39_1$", "IronSuppEffect1", names(data))
names(data) <- gsub("^Q39_2$", "IronSuppEffect2", names(data))
names(data) <- gsub("^Q39_3$", "IronSuppEffect3", names(data))
names(data) <- gsub("^Q39_4$", "IronSuppEffect4", names(data))
names(data) <- gsub("^Q39_5$", "IronSuppEffect5", names(data))
names(data) <- gsub("^Q71$", "IronSuppEffect6A", names(data))
names(data) <- gsub("^Q71_1_TEXT$", "IronSuppEffect6B", names(data))

names(data) <- gsub("^Q40_1$", "IronSuppSanq1", names(data))
names(data) <- gsub("^Q40_2$", "IronSuppSanq2", names(data))
names(data) <- gsub("^Q40_3$", "IronSuppSanq3", names(data))
names(data) <- gsub("^Q40_4$", "IronSuppSanq4", names(data))
names(data) <- gsub("^Q40_5$", "IronSuppSanq5", names(data))
names(data) <- gsub("^Q40_6$", "IronSuppSanq6", names(data))
names(data) <- gsub("^Q40_7$", "IronSuppSanq7", names(data))
names(data) <- gsub("^Q40_8$", "IronSuppSanq8", names(data))
names(data) <- gsub("^Q40_9$", "IronSuppSanq9", names(data))

names(data) <- gsub("^Q41$", "IronSuppSanqReason", names(data))
names(data) <- gsub("^Q41_3_TEXT$", "IronSuppSanqReasonB", names(data))
names(data) <- gsub("^Q77_1$", "IronDefPref1", names(data))
names(data) <- gsub("^Q77_2$", "IronDefPref2", names(data))
names(data) <- gsub("^Q77_3$", "IronDefPref3", names(data))
names(data) <- gsub("^Q77_4$", "IronDefPref4", names(data))

names(data) <- gsub("^Q79_1$", "IronSuppSanqCondition1", names(data))
names(data) <- gsub("^Q79_2$", "IronSuppSanqCondition2", names(data))
names(data) <- gsub("^Q79_3$", "IronSuppSanqCondition3", names(data))
names(data) <- gsub("^Q79_4$", "IronSuppSanqCondition4", names(data))
names(data) <- gsub("^Q79_5$", "IronSuppSanqCondition5", names(data))
names(data) <- gsub("^Q79_6$", "IronSuppSanqCondition6", names(data))

names(data) <- gsub("^Q81_1$", "IronSuppSanqReason1", names(data))
names(data) <- gsub("^Q81_2$", "IronSuppSanqReason2", names(data))
names(data) <- gsub("^Q81_3$", "IronSuppSanqReason3", names(data))
names(data) <- gsub("^Q81_4$", "IronSuppSanqReason4", names(data))
names(data) <- gsub("^Q81_5$", "IronSuppSanqReason5", names(data))

column_names <- colnames(data)
column_names <- as.data.frame(column_names)
print(column_names)
```


# Translate answers




## Mapping functions 

```{r}
#

#col 11 and 12 

f1 <- function (x){
  x <- fct_recode(x,  
                  "Disagree" = "2",
                  "Neutral"="3",
                  "Agree"="4",
                  "Totally disagree" =  "1",
                  "Totally disagree" =  "1",
                  "Totally agree" = "5"
  )
  x <- factor(
    x,
    levels = c("Totally disagree","Disagree","Neutral","Agree","Totally agree"),
    ordered = TRUE
  )
  x
}

f2 <- function (x){
  x <- fct_recode(x,  
                  "Never" = "something_in_some_language",
                  "Sometimes" = "something_in_some_language",
                  "Often" = "something_in_some_language",
                  "Always" = "Aina"
  )
  x <- factor(
    x,
    levels = c("Never","Sometimes","Often","Always"),
    ordered = TRUE
  )
  x  
}

f3 <- function (x){
  x <- fct_recode(x,  
                  "1" = "1",
                  "5" = "5"
                  )
  x <- factor(
    x,
    levels=c("1","2","3","4","5","6"),
    ordered = TRUE
  )
  x
}

f4 <- function (x){
  x <- fct_recode(x,
                  "FALSE" = "something_in_some_language",
                  "TRUE" = "something_in_some_language"
                  
                  )
  x <- factor(
    x,
    levels=c("FALSE","TRUE"),
  )
  x
}

f5 <- function (x){
  x <- fct_relevel(
    x,
    "50/50",
    "100%"
  )
x <- factor(
    x,
    levels=c("50/50","100%"),
    ordered = TRUE
  )
  x
}


f6 <- function (x){
  x <- fct_recode(x,
                  "No" = "something_in_some_language",
                  "Yes" = "something_in_some_language"
                  
                  )
  x <- factor(
    x,
    levels=c("No","Yes"),
  )
  x
}


f7 <- function (x){
  x <- as.character(x)
  x <- fct_recode(x,  
                  "FALSE" = "0",
                  "TRUE" = "1"
                  )
  x <- factor(
    x,
    levels=c("FALSE","TRUE"),
  )
  x
}

f8 <- function (x){
  x <- fct_recode(x,  
                  "Increased" = "something_in_some_language",
                  "No effect" = "something_in_some_language",
                  "Decreased" = "something_in_some_language"
  )
  x <- factor(
    x,
    levels=c("Increased","No effect","Decreased"),
  )
  x
}

f9 <- function (x){
  x <- fct_recode(x,
                  "Agree" = "something_in_some_language",
                  "Disagree" = "something_in_some_language"
                  
                  )
  x <- factor(
    x,
    levels=c("Agree","Disagree"),
  )
  x
}

f10 <- function (x){
  x <- factor(
    x,
    levels=c("1","2","3","4","5","6"),
    ordered = TRUE
  )
  x
}

f11 <- function (x){
  x <- factor(
    x,
    levels=c("1","2","3","4","5"),
    ordered = TRUE
  )
  x
}


```


## Main processing

```{r}

# Columns containing just yes and no
yesandnocols <- data %>% head(n=1) %>% mutate_all(~str_detect(.,"^No_in_some_language$")) %>% 
  bind_rows(
data %>% head(n=1) %>% mutate_all(~str_detect(.,"^yes_in_some_language$")) ) %>% 
  summarise(across(everything(), ~ any(.x)))

#Columns containing just 0 or 1
zero1cols <- data %>%  
  summarise(across(everything(), ~ str_c(names(table(.x)),collapse="") == "01"))

#Columns containing just 1-5
cols12345 <- data %>% summarise(across(everything(), ~ str_c(names(table(.x)),collapse="") == "12345"))
cols1345 <- data %>% summarise(across(everything(), ~ str_c(names(table(.x)),collapse="") == "1345"))
cols2345 <- data %>% summarise(across(everything(), ~ str_c(names(table(.x)),collapse="") == "2345"))

cols12345 <- bind_rows(cols12345,
                       cols1345,
                       cols2345) %>%  
  summarise(across(everything(), ~ any(.x))) & !str_detect(colnames(data) ,"^49\\.\\d")
#49 has scale from 1-6. But if there are no 6s then it is detected here and ruins things later



tmp <- data %>% 
  mutate(`something_in_some_language` = as.Date(`something_in_some_language`)) %>% 
  mutate( `1.0: something_in_some_language` = as.numeric(`1.0: something_in_some_language`)  ) %>%
  #here a set of questions is detected with some regular expression and then one of the
  #processing functions above is applied to process those questions
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f1(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f2(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f3(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f4(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f5(.) ) %>%
  #here instead of a regular expression, above a vector is made which tells which columns to process
  mutate_at(vars(which(as.logical(yesandnocols))), ~ f6(.) ) %>%
  mutate_at(vars(which(as.logical(zero1cols))), ~ f7(.) ) %>%
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f8(.) ) %>% 
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f9(.) ) %>%
  mutate_at(vars(which(str_detect(colnames(data) ,"something_in_some_language"))), ~ f10(.) ) %>%
  mutate_at(vars(which(cols12345)), ~ f11(.) ) %>%
  mutate(
    `2: something_in_some_language` =  fct_recode(`2: something_in_some_language`,  
                  "Male" = "something_in_some_language",
                  "Female" = "something_in_some_language",
                  "Non-binary" = "something_in_some_language",
                  "Prefer not to say" = "something_in_some_language"
                  ),
    `3: something_in_some_language?` = fct_recode(`3: something_in_some_language`,  
    "Yes" = "something_in_some_language",
    "No, due to current pregnancy" = "something_in_some_language",
    "No, due to menopause" = "something_in_some_language",
    "No, due to current contraception use" = "something_in_some_language"
     ),  
    
    `4: something_in_some_language` = fct_recode(`4: something_in_some_language?`,
                     "In a city of over 100,000 people" = "something_in_some_language",
                    "In a town of less than 100,000 people, or in the countryside" = "something_in_some_language"
                                                 
    ),
      `5: something_in_some_language?` =fct_recode(`5: something_in_some_language?`,
"None" = "something_in_some_language",
"Primary school" = "something_in_some_language", 
"High school" = "something_in_some_language",
"College" = "something_in_some_language",
"University" = "something_in_some_language",
      ) %>% fct_relevel(
        "None",
"Primary school", 
"High school",
"College",
"University"
      ) %>% as.ordered(.)
,
    `6: something_in_some_language` = fct_recode(    `6: something_in_some_language`,
"Excellent" =  "something_in_some_language",
"Very good" =  "something_in_some_language",
"Good" =   "something_in_some_language",
"Fair" =  "something_in_some_language",
"Poor" =  "Huono"
) %>% fct_relevel(.,
"Poor",
"Fair",
"Good",
"Very good",
"Excellent",  
) %>% as.ordered(.)
,
    `7: something_in_some_language` =
  str_replace_all(data$`7: something_in_some_language`,"\\(|\\)","_") %>% 
    fct_recode(.,
      "Yes, vegan (no animal products)" =  "something_in_some_language",
"Yes, vegetarian (no meat and no fish)" =  "something_in_some_language",
"Yes, pescatarian (no meat)" =  "something_in_some_language",
"Yes, flexitarian (at least three days without meat)" = "something_in_some_language" ,
"Yes, lakto-ovovegan (no meat and no fish, but milk and eggs)" = "something_in_some_language",
"No" = "something_in_some_language"

    ),    
    `8: something_in_some_language` = fct_recode(`8: something_in_some_language`,
      "1 - 3 times" = "something_in_some_language",
"4 - 10 times" = "something_in_some_language",
"More than 10 times" = "something_in_some_language",
"None" = "something_in_some_language"
    ) %>% fct_relevel(.,
    "None",
    "1 - 3 times",
"4 - 10 times",
"More than 10 times"
) %>% as.ordered(.)
,
    `9: something_in_some_language` = fct_recode(`9: something_in_some_language`,
"Within the last 6 months" =  "something_in_some_language",
"6 months to a year ago" =  "something_in_some_language",
"1-2 years ago" =  "something_in_some_language",
"I cannot remember" = "something_in_some_language",
    ) %>% fct_relevel(.,
"Within the last 6 months",
"6 months to a year ago",
"1-2 years ago",
"I cannot remember"
                      ) %>% as.ordered(.)

,
`21: something_in_some_language`
=fct_recode(`21: something_in_some_language`,
            "No" = "something_in_some_language",
            "I don’t know"= "something_in_some_language",
            "Yes, once "= "something_in_some_language",
            "Yes, multiple times "= "something_in_some_language"
            
),

`29: something_in_some_language` = 
  fct_recode(`29: something_in_some_language`,
             "I take iron supplements acquired by myself"    = "something_in_some_language",
             "I take multivitamins that contain iron "   = "something_in_some_language",
             "I take iron supplements provided by the blood service"  = "something_in_some_language",
             "I take iron supplements acquired by myself"  = "something_in_some_language",
             "I eat more iron-rich foods"    = "something_in_some_language",
             "I take iron supplements acquired by myself"   = "something_in_some_language"
  ),        
`34: something_in_some_language` =
  fct_recode(`34: something_in_some_language`,
             "Never" = "something_in_some_language",
             "Not anymore" =  "something_in_some_language",
             "Sometimes" =  "something_in_some_language",
             "Every day" =  "something_in_some_language"
  ),
`41: something_in_some_language` =
  fct_recode(`41: something_in_some_language`,
             "No, I have never taken iron (containing) supplements " = "something_in_some_language",
             "Yes, I am currently taking iron supplements ordered to me by a doctor"    = "something_in_some_language",
             "Yes, I am currently taking iron supplements from a drugstore"   =  "something_in_some_language",
             "Yes, I am currently taking iron supplements provided to me by the blood service" = "something_in_some_language", 
             "Yes, I take multivitamins that contain iron "  =  "something_in_some_language", 
             "I am taking multivitamins, but I do not know whether or not they contain iron" = "something_in_some_language",
             "I have taken iron supplements/multivitamins before, but not anymore "      = "something_in_some_language" 
             
  ),



  )
  
```


# Deal with open text answers

## 3: something_in_some_language

```{r}
tmp %>% count(`3: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


```{r}


tmp <- tmp %>%  
  mutate(
    `something_in_some_language` = str_remove_all(`something_in_some_language`,"\""), # there we some extra '\' that needed to be removed
  `3: something_in_some_language` = fct_recode(`3: something_in_some_language`,
 "No, other" =              "something_in_some_language",
 "No, other" =              "something_in_some_language",
 #... maybe some other alternative open text answers
  "No, due to menopause" =  "something_in_some_language",
# ...
   "No, due to current contraception use"  =           "something_in_some_language",
#... 
  "No, due to hysterectomy" =             "something_in_some_language",
"No, due to menopause"    =           "something_in_some_language",
  "No, other" =             "something_in_some_language",

)
)

tmp %>% count(`3: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)


```


## 5: Mikä on korkein suorittamasi koulutusaste?


```{r}
tmp %>% count(`5: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)


```

```{r}
tmp <- tmp %>% mutate(
  `5: something_in_some_language` =fct_recode(`5: something_in_some_language`,
 "High school" = "something_in_some_language",
# ... maybe some other alternatives
 "Primary school" = "something_in_some_language",
"High school" ="something_in_some_language",
"College" ="something_in_some_language",
"University" = "something_in_some_language"
),
 `5: something_in_some_language` = fct_relevel(
    `5: something_in_some_language`,
    "Primary school",
    "High school",
    "College",
    "University"
  ),
  `5: something_in_some_language` = as.ordered(
    `5: something_in_some_language`)
)

tmp %>% count(`5: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


## 24: Mistä olisit halunnut lisätietoja?


```{r}
tmp %>% count(`24: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```




```{r}
tmp <- tmp %>% mutate(
`24: something_in_some_language` = 
  fct_recode(`24: something_in_some_language`,
    "Other"= "something_in_some_language", 
    "Iron stores/ferritin" = "something_in_some_language", 
    "Other" = "something_in_some_language", 
    "Information on the consequences of low hemoglobin levels" = "something_in_some_language", 
    "Information on how to restore hemoglobin levels" = "something_in_some_language", 
    "Information on what hemoglobin is" = "something_in_some_language", 
   "No information was missing" =  "something_in_some_language" 

  ),
)

```


```{r}
tmp %>% count(`24: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


## 36: Onko olemassa jokin muu syy, miksi käytät tai olet käyttänyt ravintolisiä?`


```{r}
tmp %>% count(`36: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```



```{r}
tmp <- tmp %>% mutate(
  `36: something_in_some_language` =
    case_when(
      !is.na(`36: something_in_some_language`) & 
        `36: something_in_some_language` != "No" ~ "Other",
      TRUE ~ `36: something_in_some_language`
          ),        
   `36: something_in_some_language` = 
    as_factor(`36: something_in_some_language`)    

)
```


```{r}
tmp %>% count(`36: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


## 44: Askarruttaako jokin muu rautalisiin liittyvä asia sinua?


```{r}
tmp %>% count(`44: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)

```


```{r}
tmp <- tmp %>% mutate(
  `44: something_in_some_language` =
    case_when(
      !is.na(`44: something_in_some_language`) & 
        `44: something_in_some_language` != "No" ~ "Other",
      TRUE ~ `44: something_in_some_language`
          ),        
   `44: something_in_some_language` = 
    as_factor(`44: something_in_some_language`)
)
```


```{r}
tmp %>% count(`44: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```

## 46: Mikä on sinulle tärkein syy ottaa vastaan Veripalvelun tarjoama rautalisä?


```{r}
tmp %>% count(`46: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


```{r}
tmp <- tmp %>% mutate(
  `46: something_in_some_language` =
    fct_recode(`46: something_in_some_language`,
               "To improve my health" = "something_in_some_language",
               # ... maybe some alternative ansers
               "To be able to donate without delays" = "something_in_some_language",
               "I would never take them" = "something_in_some_language" ,
               "To improve my health" = "something_in_some_language",
               "Other" = "something_in_some_language",
               "Other" = "something_in_some_language",
               "To recover from donation" = "something_in_some_language"
    )
)


```



```{r}
tmp %>% count(`46: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


## Removed open texts

### 37.1: Voisitko harkita ravintolisien käyttöä?: Kyllä, koska

```{r}
tmp %>% count(`37.1: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
```


### 37.2: Voisitko harkita ravintolisien käyttöä?: En, koska

```{r}
tmp %>% count(`37.2: something_in_some_language`) %>% arrange(desc(n)) %>% print( n = 1e3)
 
```


```{r}

```




```{r}
summary(tmp)
```




## Translate questions

```{r}

questions <- read_excel("../data/Tulokset - Donor Perception Survey question translations (ID 125823).xlsx")
questions <- questions %>% 
  mutate(
    QuestionWNo = str_c(str_extract(Kysymys, "^.*\\d+\\:")," ",Question) %>% str_replace("\\.0\\:",":") %>% 
      str_replace("\\.$","") %>% str_replace_all("\\.\\:",":") 
  )


```


```{r}
data <- tmp %>% select(-`Päivämäärä`)
colnames(data) <- questions$QuestionWNo

#Remove 37.1 and 37.2
data <- data %>% 
  select(-(which(str_detect(colnames(data) ,"^37\\.\\d"))))

save(data,file="../results/donorironpercep.rdata")
```

```{r}

colclasses <- data %>% ungroup %>% summarise(across(everything(), ~ class(.x))) %>% t() %>% as_tibble(rownames="col")

colclasses %>% count(V1)

```




# Summarise 


```{r}
dfSummary(data,
          plain.ascii = FALSE, 
          style = "grid", 
          graph.col = TRUE,
          graph.magnif = 0.75, 
          valid.col = FALSE, 
          tmp.img.dir = "/tmp")


```

